Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-22 prop_letter.tex
prop_letter.tex \section{Gleason} Reviewing...

While the finite-precision extension of Kochen-Specker theorem asserts
the non-existence of certain kind of QIVPMs, we also want to understand
what a QIVPM could be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the state~$\proj{\ps}$.
The way we extending a state to a QIVPM will first be generalized
in this section, and introduce a finite-precision extension of the
Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. The
Born rule is essential to compute the conventional quantum probability
because any quantum probability measure can be induced by the Born
rule according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
We then provide a finite precision variant of Gleason's theorem for
the Born QIVPMs, but there are also some general QIVPMs may not be
induced by any quantum probability measure, i.e., no state is consistent
with these kind of QIVPMs.

>>>>

While the finite-precision extension of Kochen-Specker theorem asserts
the non-existence of certain kind of QIVPMs, we also want to understand
what a QIVPM could be when it exists. A conventional quantum probability
measure can be easily be constructed using the Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}
from a unique state, and this is the only way to construct a conventional
quantum probability measure according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.

In Sec.~\ref{sec:Interval-Uncertainty}, the only non-trivial QIVPM~
$\bar{\mu}_{3}$ is induced by the state~$\proj{\ps}$. The way we
extending a state to a QIVPM will first be generalized in this section,
and introduce a finite-precision extension of the Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
The Born rule is essential to compute the conventional quantum probability
because any quantum probability measure can be induced by the Born
rule according to Gleason's theorem~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
We then provide a finite precision variant of Gleason's theorem for
the Born QIVPMs, but there are also some general QIVPMs may not be
induced by any quantum probability measure, i.e., no state is consistent
with these kind of QIVPMs.
